Hybrid platforms and bargaining

### 2023-06-11 src/presentation/io_day.qmd
Add IO day presentation

---
title: "Hybrid platforms and bargaining"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        html-math-method: mathjax
        transition: fade
        touch: true
        toc: true
        toc-depth: 1
        toc-title: Agenda
        slide-number: c
        progress: true
        controls: false
        theme:
         - default
         - css/custom.scss
        include-in-header:
         - js/mathjax-settings.html
bibliography: references.bib
---

>>>>

---
title: "Hybrid platforms and bargaining"
subtitle: "Swiss IO day 2023"
author:
  - name: Martin Stancsics
    email: martin.stancsics@econ.uzh.ch
    affiliations:
      - name: University of Zürich
date: 2023-06-16
date-format: long
format:
    revealjs:
        embed-resources: true
        html-math-method: mathjax
        transition: fade
        touch: true
        toc: true
        toc-depth: 1
        toc-title: Agenda
        slide-number: c
        progress: true
        controls: false
        theme:
         - default
         - css/custom.scss
        include-in-header:
         - js/mathjax-settings.html
bibliography: references.bib
---
